---
title: 'AICs and BICs for selecting models'
output:
  html_document:
    code_folding: hide
    highlight: tango
    theme: united
    toc: yes
    toc_depth: 4
    toc_float: yes
editor_options:
  chunk_output_type: console
---

```{r options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE, comment = FALSE, 
                      cache.lazy = FALSE)
options(scipen=999)
options(knitr.kable.NA = '')
```

```{r package, include=FALSE}
# package -----
library(kableExtra)
library(dplyr)
library(tidyr)
library(ggplot2)
library(rms)
library(stargazer)
library(ggstance)
library(stringr)
library(knitr)
library(purrr)
```

```{r data, include=FALSE}


load("1 data prep/working data.RData")


# to all variable in the environment, group age, select complete cases, group obesity

e<-eapply(.GlobalEnv, function(x) {
  x<-x%>%
    filter(!is.na(bmi.all_time_gr))%>%
    mutate(age_gr.b= ifelse(age<=59, "Aged 18 to 59",
                            ifelse(age<=79, "Aged 60 to 79",
                                   "Aged 80 or above" ))) %>%
    mutate(age_gr.b = factor(age_gr.b, levels = c("Aged 18 to 59", "Aged 60 to 79","Aged 80 or above"))) %>%
    filter(!is.na(smoke.all_time))%>%
    mutate(smoke.all_time=factor(smoke.all_time))%>%
    mutate(smoke.all_time=relevel(smoke.all_time, "Never smoker"))%>%
    filter(!is.na(medea))%>%
    mutate(medea=relevel(medea, "U1"))%>%
    droplevels()
  levels(x$bmi.all_time_gr)<-list("normal or underweight"="normal or underweight",
                                  "overweight" ="overweight",
                                  "obese"=c("obese class I", "obese class II", "obese class III"))
  output <- x
}
)

nms <- names(e)
for ( n in nms ){
  assign(n, e[[n]])
}

#load functions
source("functions_hazardratio.R") 

```



```{r, cache=TRUE}
# get models -----

models.healthy.diagnosis<-get.models(r.healthy.diagnosis, "healthy.diagnosis")
models.healthy.hospitalised<-get.models(r.healthy.hospitalised, "healthy.hospitalised")
models.diagnosis.hospitalised<-get.models(r.diagnosis.hospitalised, "diagnosis.hospitalised")
models.diagnosis.death<-get.models(r.diagnosis.death, "diagnosis.death")
models.hospitalised.death<-get.models(r.hospitalised.death, "hospitalised.death")

```

# Transition 1: From general population to diagnosed with COVID-19 
```{r}
# models and relative hazards from models -----
r.hazard<-get.r.hazard(model=models.healthy.diagnosis,
                       bmi.1=22,
                       bmi.2=seq(15,60, 1)) 

```

## Principal analysis
```{r}
fit<-fit.fun(r.hazard)

fit<-fit %>%
  pivot_wider(names_from = name, 
              values_from = c(aic,bic)) 
fit<-fit %>%
  select(type ,       
         aic_overall.bmi.only, bic_overall.bmi.only,
         aic_overall.bmi.age.gender,bic_overall.bmi.age.gender,
         aic_overall.bmi.complete, bic_overall.bmi.complete,
         
         aic_firstage.bmi.only, bic_firstage.bmi.only,
         aic_firstage.bmi.age.gender,bic_firstage.bmi.age.gender,
         aic_firstage.bmi.complete, bic_firstage.bmi.complete,
         
         aic_secondage.bmi.only, bic_secondage.bmi.only,
         aic_secondage.bmi.age.gender,bic_secondage.bmi.age.gender,
         aic_secondage.bmi.complete, bic_secondage.bmi.complete,
         
         aic_thirdage.bmi.only, bic_thirdage.bmi.only,
         aic_thirdage.bmi.age.gender,bic_thirdage.bmi.age.gender,
         aic_thirdage.bmi.complete, bic_thirdage.bmi.complete,
         
         aic_female.bmi.only, bic_female.bmi.only,
         aic_female.bmi.age.gender,bic_female.bmi.age.gender,
         aic_female.bmi.complete, bic_female.bmi.complete,
         
         aic_male.bmi.only, bic_male.bmi.only,
         aic_male.bmi.age.gender,bic_male.bmi.age.gender,
         aic_male.bmi.complete, bic_male.bmi.complete
  )

kable(fit %>% 
        mutate(type=ifelse(type=="rcs3",
                           "restricted cubic spline (3 knots)",
                           ifelse(type=="rcs4",
                                  "restricted cubic spline (4 knots)",
                                  ifelse(type=="rcs5",
                                         "restricted cubic spline (5 knots)",      
                                         type)))), 
      col.names = c("Type",  
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC"))  %>%
  kable_styling(bootstrap_options = c("striped", "bordered"))  %>%
  add_header_above( c("",
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2
                      
  ))  %>%
  add_header_above( c("",
                      "Overall" = 6,
                      "Aged 18 to 59" = 6,
                      "Aged 60 to 79" = 6,
                      "Aged 80 or above"=6,
                      "Female" = 6,
                      "Male" = 6))%>%
  add_header_above(
    c("From general population to diagnosed with COVID-19" = 37))
```

## Secondary analysis
### Stratifying for month
```{r}
fit<-rbind(
  #march - complete
  r.hazard %>% 
    filter(str_detect(model, ".march")) %>% 
    filter(str_detect(model, ".bmi.complete")) %>% 
    select(model, aic, bic) %>% 
    distinct() %>% 
    mutate(bic=nice.num(bic)) %>% 
    mutate(aic=nice.num(aic)) %>% 
    mutate(type=str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse="|"))) %>% 
    select(type, aic, bic) %>% 
    mutate(name="march.bmi.complete"),
  
  #april - complete
  r.hazard %>% 
    filter(str_detect(model, ".april")) %>% 
    filter(str_detect(model, ".bmi.complete")) %>% 
    select(model, aic, bic) %>% 
    distinct() %>% 
    mutate(bic=nice.num(bic)) %>% 
    mutate(aic=nice.num(aic)) %>% 
    mutate(type=str_extract(model, paste(c("linear", "quadratic", "rcs3", "rcs4", "rcs5"), collapse="|"))) %>% 
    select(type, aic, bic) %>% 
    mutate(name="april.bmi.complete"))

fit<-fit %>%
  pivot_wider(names_from = name, 
              values_from = c(aic,bic)) 
fit<-fit %>%
  select(type ,
         aic_march.bmi.complete, bic_march.bmi.complete,
         aic_april.bmi.complete, bic_april.bmi.complete
  )

kable(fit %>% 
        mutate(type=ifelse(type=="rcs3",
                           "restricted cubic spline (3 knots)",
                           ifelse(type=="rcs4",
                                  "restricted cubic spline (4 knots)",
                                  ifelse(type=="rcs5",
                                         "restricted cubic spline (5 knots)",      
                                         type)))), 
      col.names = c("Type",  
                    "AIC","BIC", "AIC","BIC"))  %>%
  kable_styling(bootstrap_options = c("striped", "bordered"))  %>%
  add_header_above( c("", "Complete adjustment" = 2, "Complete adjustment" = 2))  %>%
  add_header_above( c("","March"=2,"April"=2))%>%
  add_header_above( c("From general population to diagnosed with COVID-19" = 5))
```

# Transition 2: From general population to hospitalised with COVID-19 
```{r}
# models and relative hazards from models -----
r.hazard<-get.r.hazard(model=models.healthy.hospitalised,
                       bmi.1=22,
                       bmi.2=seq(15,60, 1)) 

```

## Principal analysis
```{r}
fit<-fit.fun(r.hazard)

fit<-fit %>%
  pivot_wider(names_from = name, 
              values_from = c(aic,bic)) 
fit<-fit %>%
  select(type ,       
         aic_overall.bmi.only, bic_overall.bmi.only,
         aic_overall.bmi.age.gender,bic_overall.bmi.age.gender,
         aic_overall.bmi.complete, bic_overall.bmi.complete,
         
         aic_firstage.bmi.only, bic_firstage.bmi.only,
         aic_firstage.bmi.age.gender,bic_firstage.bmi.age.gender,
         aic_firstage.bmi.complete, bic_firstage.bmi.complete,
         
         aic_secondage.bmi.only, bic_secondage.bmi.only,
         aic_secondage.bmi.age.gender,bic_secondage.bmi.age.gender,
         aic_secondage.bmi.complete, bic_secondage.bmi.complete,
         
         aic_thirdage.bmi.only, bic_thirdage.bmi.only,
         aic_thirdage.bmi.age.gender,bic_thirdage.bmi.age.gender,
         aic_thirdage.bmi.complete, bic_thirdage.bmi.complete,
         
         aic_female.bmi.only, bic_female.bmi.only,
         aic_female.bmi.age.gender,bic_female.bmi.age.gender,
         aic_female.bmi.complete, bic_female.bmi.complete,
         
         aic_male.bmi.only, bic_male.bmi.only,
         aic_male.bmi.age.gender,bic_male.bmi.age.gender,
         aic_male.bmi.complete, bic_male.bmi.complete
         
         
  )


kable(fit %>% 
        mutate(type=ifelse(type=="rcs3",
                           "restricted cubic spline (3 knots)",
                           ifelse(type=="rcs4",
                                  "restricted cubic spline (4 knots)",
                                  ifelse(type=="rcs5",
                                         "restricted cubic spline (5 knots)",      
                                         type)))), 
      col.names = c("Type",  
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC"))  %>%
  kable_styling(bootstrap_options = c("striped", "bordered"))  %>%
  add_header_above( c("",
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2
                      
  ))  %>%
  add_header_above( c("",
                      "Overall" = 6,
                      "Aged 18 to 59" = 6,
                      "Aged 60 to 79" = 6,
                      "Aged 80 or above"=6,
                      "Female" = 6,
                      "Male" = 6))%>%
  add_header_above(
    c("From general population to hospitalised with COVID-19" = 37))
```



# Transition 4: From diagnosed with COVID-19 to hospitalised with COVID-19 
```{r}
# models and relative hazards from models -----
r.hazard<-get.r.hazard(model=models.diagnosis.hospitalised,
                       bmi.1=22,
                       bmi.2=seq(15,60, 1)) 

```

## Principal analysis
```{r}
fit<-fit.fun(r.hazard)

fit<-fit %>%
  pivot_wider(names_from = name, 
              values_from = c(aic,bic)) 
fit<-fit %>%
  select(type ,       
         aic_overall.bmi.only, bic_overall.bmi.only,
         aic_overall.bmi.age.gender,bic_overall.bmi.age.gender,
         aic_overall.bmi.complete, bic_overall.bmi.complete,
         
         aic_firstage.bmi.only, bic_firstage.bmi.only,
         aic_firstage.bmi.age.gender,bic_firstage.bmi.age.gender,
         aic_firstage.bmi.complete, bic_firstage.bmi.complete,
         
         aic_secondage.bmi.only, bic_secondage.bmi.only,
         aic_secondage.bmi.age.gender,bic_secondage.bmi.age.gender,
         aic_secondage.bmi.complete, bic_secondage.bmi.complete,
         
         aic_thirdage.bmi.only, bic_thirdage.bmi.only,
         aic_thirdage.bmi.age.gender,bic_thirdage.bmi.age.gender,
         aic_thirdage.bmi.complete, bic_thirdage.bmi.complete,
         
         aic_female.bmi.only, bic_female.bmi.only,
         aic_female.bmi.age.gender,bic_female.bmi.age.gender,
         aic_female.bmi.complete, bic_female.bmi.complete,
         
         aic_male.bmi.only, bic_male.bmi.only,
         aic_male.bmi.age.gender,bic_male.bmi.age.gender,
         aic_male.bmi.complete, bic_male.bmi.complete
         
         
  )


kable(fit %>% 
        mutate(type=ifelse(type=="rcs3",
                           "restricted cubic spline (3 knots)",
                           ifelse(type=="rcs4",
                                  "restricted cubic spline (4 knots)",
                                  ifelse(type=="rcs5",
                                         "restricted cubic spline (5 knots)",      
                                         type)))), 
      col.names = c("Type",  
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC"))  %>%
  kable_styling(bootstrap_options = c("striped", "bordered"))  %>%
  add_header_above( c("",
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2
                      
  ))  %>%
  add_header_above( c("",
                      "Overall" = 6,
                      "Aged 18 to 59" = 6,
                      "Aged 60 to 79" = 6,
                      "Aged 80 or above"=6,
                      "Female" = 6,
                      "Male" = 6))%>%
  add_header_above(
    c("From diagnosed with COVID-19 to hospitalised with COVID-19" = 37))
```



# Transition 5: From diagnosed with COVID-19 to death 
```{r}
# models and relative hazards from models -----
r.hazard<-get.r.hazard(model=models.diagnosis.death,
                       bmi.1=22,
                       bmi.2=seq(15,60, 1)) 

```

## Principal analysis
```{r}
fit<-fit.fun(r.hazard)

fit<-fit %>%
  pivot_wider(names_from = name, 
              values_from = c(aic,bic)) 
fit<-fit %>%
  select(type ,       
         aic_overall.bmi.only, bic_overall.bmi.only,
         aic_overall.bmi.age.gender,bic_overall.bmi.age.gender,
         aic_overall.bmi.complete, bic_overall.bmi.complete,
         
         aic_firstage.bmi.only, bic_firstage.bmi.only,
         aic_firstage.bmi.age.gender,bic_firstage.bmi.age.gender,
         aic_firstage.bmi.complete, bic_firstage.bmi.complete,
         
         aic_secondage.bmi.only, bic_secondage.bmi.only,
         aic_secondage.bmi.age.gender,bic_secondage.bmi.age.gender,
         aic_secondage.bmi.complete, bic_secondage.bmi.complete,
         
         aic_thirdage.bmi.only, bic_thirdage.bmi.only,
         aic_thirdage.bmi.age.gender,bic_thirdage.bmi.age.gender,
         aic_thirdage.bmi.complete, bic_thirdage.bmi.complete,
         
         aic_female.bmi.only, bic_female.bmi.only,
         aic_female.bmi.age.gender,bic_female.bmi.age.gender,
         aic_female.bmi.complete, bic_female.bmi.complete,
         
         aic_male.bmi.only, bic_male.bmi.only,
         aic_male.bmi.age.gender,bic_male.bmi.age.gender,
         aic_male.bmi.complete, bic_male.bmi.complete
  )


kable(fit %>% 
        mutate(type=ifelse(type=="rcs3",
                           "restricted cubic spline (3 knots)",
                           ifelse(type=="rcs4",
                                  "restricted cubic spline (4 knots)",
                                  ifelse(type=="rcs5",
                                         "restricted cubic spline (5 knots)",      
                                         type)))), 
      col.names = c("Type",  
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC"))  %>%
  kable_styling(bootstrap_options = c("striped", "bordered"))  %>%
  add_header_above( c("",
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2
                      
  ))  %>%
  add_header_above( c("",
                      "Overall" = 6,
                      "Aged 18 to 59" = 6,
                      "Aged 60 to 79" = 6,
                      "Aged 80 or above"=6,
                      "Female" = 6,
                      "Male" = 6))%>%
  add_header_above(
    c("From diagnosed with COVID-19 to death" = 37))
```



# Transition 6: From hospitalised with COVID-19 to death 
```{r}
# models and relative hazards from models -----
r.hazard<-get.r.hazard(model=models.hospitalised.death,
                       bmi.1=22,
                       bmi.2=seq(15,60, 1)) 

```
## Principal analysis
```{r}
## Comparison of alternative models
### Model fit
fit<-fit.fun(r.hazard)

fit<-fit %>%
  pivot_wider(names_from = name, 
              values_from = c(aic,bic)) 
fit<-fit %>%
  select(type ,       
         aic_overall.bmi.only, bic_overall.bmi.only,
         aic_overall.bmi.age.gender,bic_overall.bmi.age.gender,
         aic_overall.bmi.complete, bic_overall.bmi.complete,
         
         aic_firstage.bmi.only, bic_firstage.bmi.only,
         aic_firstage.bmi.age.gender,bic_firstage.bmi.age.gender,
         aic_firstage.bmi.complete, bic_firstage.bmi.complete,
         
         aic_secondage.bmi.only, bic_secondage.bmi.only,
         aic_secondage.bmi.age.gender,bic_secondage.bmi.age.gender,
         aic_secondage.bmi.complete, bic_secondage.bmi.complete,
         
         aic_thirdage.bmi.only, bic_thirdage.bmi.only,
         aic_thirdage.bmi.age.gender,bic_thirdage.bmi.age.gender,
         aic_thirdage.bmi.complete, bic_thirdage.bmi.complete,
         
         aic_female.bmi.only, bic_female.bmi.only,
         aic_female.bmi.age.gender,bic_female.bmi.age.gender,
         aic_female.bmi.complete, bic_female.bmi.complete,
         
         aic_male.bmi.only, bic_male.bmi.only,
         aic_male.bmi.age.gender,bic_male.bmi.age.gender,
         aic_male.bmi.complete, bic_male.bmi.complete
         
         
  )


kable(fit %>% 
        mutate(type=ifelse(type=="rcs3",
                           "restricted cubic spline (3 knots)",
                           ifelse(type=="rcs4",
                                  "restricted cubic spline (4 knots)",
                                  ifelse(type=="rcs5",
                                         "restricted cubic spline (5 knots)",      
                                         type)))), 
      col.names = c("Type",  
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC",
                    "AIC","BIC", "AIC","BIC", "AIC","BIC"))  %>%
  kable_styling(bootstrap_options = c("striped", "bordered"))  %>%
  add_header_above( c("",
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2, 
                      "Unadjusted" = 2, "Adjusted for age and gender" = 2,"Complete adjustment" = 2
                      
  ))  %>%
  add_header_above( c("",
                      "Overall" = 6,
                      "Aged 18 to 59" = 6,
                      "Aged 60 to 79" = 6,
                      "Aged 80 or above"=6,
                      "Female" = 6,
                      "Male" = 6))%>%
  add_header_above(
    c("From hospitalised with COVID-19 to death" = 37))
```





